\documentclass[a4paper,11pt,twoside]{pads-thesis}

%%%%% PACKAGES USED SORTED ALPHABETICALLY  %%%%%
\usepackage[toc,page]{appendix} % support appendices
\usepackage{csquotes} % handles quotes automatically
\usepackage{hyperref} % allows autoref/hyperlinks/etc.
\usepackage{amsmath}
\usepackage{stmaryrd}


%%%%% PADS TEMPLATE SETTINGS %%%%%
\renewcommand{\gTitle}{Estimating Probabilities for Realizations of Uncertain Event Data}
\renewcommand{\gAuthor}{Bianka Bakullari}
\renewcommand{\gStudentID}{363085}
\renewcommand{\gHeader}{Master's Thesis}
\renewcommand{\gSupervisor}{
    Marco Pegoraro M.Sc.}
\renewcommand{\gExaminer}{Prof. Wil van der Aalst \\ 
	Prof. Joost-Pieter Katoen }
\renewcommand{\gInstitution}{i9 Process and Data Science (PADS) Chair, RWTH Aachen University}
%\renewcommand{\gRegDate}{YYYY-MM-DD}
%\renewcommand{\gSubDate}{YYYY-MM-DD}

%%%%% AUTOREF %%%%%
\renewcommand{\sectionautorefname}{Section}

\begin{document}
%%% Title page
\pagenumbering{roman}

\gTitlePage
%\pagestyle{plain}
%%% TOC

%\begin{abstract}
\chapter*{Abstract} \addcontentsline{toc}{chapter}{Abstract}
\input{chapters/abstract.tex}\label{chap: abstract}
%\end{abstract}

\tableofcontents

%\setcounter{page}{1}
\cleardoublepage
%%% Begin document
\pagestyle{fancy}
\pagenumbering{arabic}

\chapter{Introduction} \label{chap:intro}
\input{chapters/introduction.tex}

\chapter{Related Work} \label{chap:related_work}
\input{chapters/related_work.tex}

\chapter{Preliminaries} \label{chap:prelim}
\input{chapters/prelim.tex}

\chapter{Process Mining Over Uncertain Data} \label{chap:fundamentals}
\input{chapters/fundamentals.tex}

\chapter{Trace Realizations of Uncertain Process Instances} \label{chap:realizations}
\input{chapters/realizations.tex}

\chapter{Estimating Probabilities for Trace Realizations}
\label{chap:estimates}
\input{chapters/estimates.tex}


%\chapter{Evaluation} \label{chap:eval}
%\input{chapters/evaluation.tex}

%\chapter{Discussion} \label{chap:discussion}
%\input{chapters/discussion.tex}

\chapter{Conclusion} \label{chap:conclusion}
\input{chapters/conclusion.tex}

%\bibliography{references} 
%\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{5}

\bibitem{pm4py}
Pm4Py, \url{http://pm4py.pads.rwth-aachen.de/}

\bibitem{proved}
PROVED, \url{https://github.com/proved-py/proved-core/}

\bibitem{pm}
Van der Aalst, W.M.P.: Process mining: data science in action. Springer (2016)

\bibitem{mining}
Pegoraro, M., van der Aalst, W.M.P.: Mining Uncertain Event Data in Process Mining. In: 2019 International Conference on Process Mining (ICPM). pp. 89-96. IEEE (2019).

\bibitem{discovery}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Discovering process models from uncertain event data. In: International Conference on Business Process Management. pp. 238-249. Springer (2019)

\bibitem{efficient}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Efficient construction of behavior graphs for uncertain event data. In: International Conference on Business Information Systems (BIS). Springer (2020).

\bibitem{conformance}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Conformance checking over Uncertain Event Data (2020).

\bibitem{space}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Efficient Time and Space Representation of Uncertain Event Data (2020). 

\bibitem{por}
Van der Aa, H., Leopold, H., Weidlich, M.: Partial order resolution of event logs for process conformance checking. Decision Support Systems p. 113347 (2020)

\bibitem{alignment}
Adriansyah, A.: Aligning observed and modeled behavior (2014).

\bibitem{transitive}
Aho, A.V., Garey, M.R., Ullman, J.D.: The transitive reduction of a directed graph.
SIAM Journal on Computing 1(2), 131-137 (1972).

\bibitem{pm4py_book}
Berti, A., van Zelst, S.J., van der Aalst, W.M.P.: Process Mining for Python (PM4Py): Bridging the Gap Between Process- and Data Science. In: ICPM Demo Track (CEUR 2374). p. 1316 (2019).

\bibitem{xixi}
X. Lu, D. Fahland, W. M. P. van der Aalst, Conformance checking based on partially ordered event data, in: International conference on business process management, Springer, 2014, pp. 75–88.

\bibitem{earth}
S. J. Leemans,W. M. van der Aalst, T. Brockhoff, A. Polyvyanyy, Stochastic process mining: Earth movers stochastic conformance, Information Systems (101724) (2021).

\bibitem{repair}
R. Conforti, M. La Rosa, A. H. Ter Hofstede, A. Augusto, Automatic repair of same-timestamp errors in business
process event logs, in: International Conference on Business Process Management, Springer, 2020, pp. 327–345.

\bibitem{distributed}
I. Beschastnikh, Y. Brun, M. D. Ernst, A. Krishnamurthy, T. E. Anderson, Mining temporal invariants from partially ordered logs, in: Managing Large-scale Systems via the Analysis of System Logs and the Application of Machine Learning Techniques, 2011, pp. 1–10.




\end{thebibliography}


%\begin{appendices}
    %\chapter{Some Appendix}
    %Try to avoid appendices.
    %If you can't this is a place to show all kinds of results that are supportive, yet, not critical for your thesis.
%\end{appendices}



%\chapter*{Acknowledgments}\addcontentsline{toc}{chapter}{Acknowledgements}
%\input{chapters/acknowledgements.tex}



\end{document}