\begin{thebibliography}

\bibitem{pm4py}
Pm4Py, \url{http://pm4py.pads.rwth-aachen.de/}

\bibitem{proved}
PROVED, \url{https://github.com/proved-py/proved-core/}

\bibitem{pm}
van der Aalst, W.M.P.: Process mining: data science in action. Springer (2016)

\bibitem{mining}
Pegoraro, M., van der Aalst, W.M.P.: Mining Uncertain Event Data in Process Mining. In: 2019 International Conference on Process Mining (ICPM). pp. 89-96. IEEE (2019).

\bibitem{discovery}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Discovering process models from uncertain event data. In: International Conference on Business Process Management. pp. 238-249. Springer (2019)

\bibitem{efficient}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Efficient construction of behavior graphs for uncertain event data. In: International Conference on Business Information Systems (BIS). Springer (2020).

\bibitem{conformance}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Conformance checking over Uncertain Event Data (2020).

\bibitem{space}
Pegoraro, M., Uysal, M.S., van der Aalst, W.M.P.: Efficient Time and Space Representation of Uncertain Event Data (2020). 

\bibitem{por}
van der Aa, H., Leopold, H., Weidlich, M.: Partial order resolution of event logs for process conformance checking. Decision Support Systems p. 113347 (2020)

\bibitem{alignment}
A. Adriansyah, Aligning observed and modeled behavior, Ph.D. thesis, Eindhoven University of Technology (2014).

\bibitem{transitive}
Aho, A.V., Garey, M.R., Ullman, J.D.: The transitive reduction of a directed graph.
SIAM Journal on Computing 1(2), 131-137 (1972).

\bibitem{pm4py_book}
Berti, A., van Zelst, S.J., van der Aalst, W.M.P.: Process Mining for Python (PM4Py): Bridging the Gap Between Process- and Data Science. In: ICPM Demo Track (CEUR 2374). p. 1316 (2019).

\bibitem{xixi}
X. Lu, D. Fahland, W. M. P. van der Aalst, Conformance checking based on partially ordered event data, in: International conference on business process management, Springer, 2014, pp. 75–88.

\bibitem{earth}
S.J.J. Leemans, A.F. Syring, and W.M.P. van der Aalst. Earth Movers’ Stochastic Conformance Checking. In T.T. Hildebrandt, B.F. van Dongen, M. Röglinger, and J. Mendling, editors, Business Process Management Forum (BPM Forum 2019), volume 360 of Lecture Notes in Business Information Processing, pages 127-143. Springer-Verlag, Berlin, 2019.

\bibitem{repair}
R. Conforti, M. La Rosa, A. H. Ter Hofstede, A. Augusto, Automatic repair of same-timestamp errors in business
process event logs, in: International Conference on Business Process Management, Springer, 2020, pp. 327–345.

\bibitem{distributed}
I. Beschastnikh, Y. Brun, M. D. Ernst, A. Krishnamurthy, T. E. Anderson, Mining temporal invariants from partially ordered logs, in: Managing Large-scale Systems via the Analysis of System Logs and the Application of Machine Learning Techniques, 2011, pp. 1–10.




\end{thebibliography}